Automated topic naming to support analysis of software maintenance activities

### 2010-08-20 icse/icse2011.tex
threats to validity

\subsection{Threats to validity}
\emph{Construct validity} issues include that we used only commit messages rather than mail or bug tracker messages. We also chose our taxonomy and the data to study. \emph{Internal validity} issues are to do with inter-rater reliability. \emph{External validity} issues are that our data originated from OSS database projects and thus might not be applicable to commercially developed software. Furthermore, our analysis techniques rely on a project's use of meaningful commit messages.
\todo[inline]{update this with more detail}

>>>>

\subsection{Threats to validity}

\emph{Construct validity} issues include that we used only commit messages rather than mail or bug tracker messages. 
We also chose our taxonomy and the data to study. Also, we did not show these results to the stakeholders.

\emph{Internal validity} issues are include inter-rater reliability and our lack of rival explanation building. 
We improved internal validity by trying to correlate and explain the behaviours observed in the analysis with the historical records of the projects.

\emph{External validity} was addressed by our use of multiple case studies, but there are still issues. 
Our data originated from OSS database projects and thus might not be applicable to commercially developed software. 
Furthermore, our analysis techniques rely on a project's use of meaningful commit messages.

% in Case Study Research: Design Case Studies
\emph{Reliability} was addressed by each annotator following the same protocol and using the same annotations. 
Unfortunately only two annotators were used, their annotating could be biased and we did not analyze for inter-rater reliability.

%\todo[inline]{update this with more detail}
